---
title: "Veonetal_BM_BC_Analyses"
author: "John Veon"
date: "2023-04-01"
output: html_document
---

###Read in data file###
```{r}
BCI30km <- read.csv("./MALL_BM_BCI_AR_LMAV_2019_2021.csv", header = TRUE)
library(ggplot2)
library(ggfortify) 
library(MASS)
library(ggthemes)
library(lme4)
library(car)
library(AICcmodavg)
library(lattice)
library(rstatix)
library(MuMIn)
library(ggeffects)
library(lmerTest)
library(corrplot)
library(redres)
```


##Make variables
```{r}
BCI30km$LOC_NUM_BCI = as.factor(BCI30km$LOC_NUM_BCI)

BCI30km$PropTotWaterl = log(BCI30km$PropTotWater)
BCI30km$PropSoybeanl = log(BCI30km$PropSoybean)
BCI30km$PropHerbWetl = log(BCI30km$PropHerbWet)
BCI30km$Prop_MedDisturbl = log(BCI30km$Prop_MedDisturb)
```

```{r}
BCI30km$PropTotWaterls = scale(BCI30km$PropTotWaterl)
BCI30km$PropWoodyWets = scale(BCI30km$PropWoodyWet)
BCI30km$PropRices = scale(BCI30km$PropRice)
BCI30km$PropSoybeanls = scale(BCI30km$PropSoybeanl)
BCI30km$PropHerbWetls = scale(BCI30km$PropHerbWetl)
BCI30km$Prop_MedDisturbls = scale(BCI30km$Prop_MedDisturbl)
```

###Correlation Matrix###
```{r}
# Load data
my_CorBCI <- BCI30km[, c(12,14,16,17,19,20,21,22,23,24)]
# print the first 6 rows
head(my_CorBCI, 9)
```

```{r}
res2OP <- cor(my_CorBCI,use = "complete.obs", method = "pearson")
round(res2OP, 2)
corrplot(res2OP, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

###Model Development
####Body Mass (note there are similar naming conventions between mass and condition code; rerun each analysis fully before running result/figure code to ensure the correct data is being read in)###
```{r}
##run models
##Note: Restricted Maximum Likelihood REML set to False. REML Fitting is only appropriate for GLMMs (glmer). Since we are using LMM's (lmer), we want the regular Maximum Liklihood (ML) Fitting.

##Rice and Water
BCImod11<-lmer(CS_BM ~ PropTotWaterls + PropRices + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Soy and Water
BCImod21<-lmer(CS_BM ~ PropTotWaterls + PropSoybeanls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Woody and Water
BCImod31<-lmer(CS_BM ~ PropTotWaterls + PropWoodyWets + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Herb and Water
BCImod41<-lmer(CS_BM ~ PropTotWaterls + PropHerbWetls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Dist and Water
BCImod51<-lmer(CS_BM ~ PropTotWaterls + Prop_MedDisturbls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Ag Only
BCImod61<-lmer(CS_BM ~PropTotWaterls + PropRices + PropSoybeanls + (1 | LOC_NUM_BCI), data=BCI30km,REML = F)

#Natural Wetlands
BCImod71 <- lmer(CS_BM ~ PropTotWaterls + PropWoodyWets + PropHerbWetls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

###Agriculture and Disturbance
BCImod81 <- lmer(CS_BM ~ PropTotWaterls + PropRices + PropSoybeanls + Prop_MedDisturbls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Natural Wetlands and Disturbance
BCImod91 <- lmer(CS_BM ~ PropTotWaterls + PropWoodyWets + PropHerbWetls + Prop_MedDisturbls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##All Habitat
BCImod101 <- lmer(CS_BM ~ PropTotWaterls + PropRices + PropSoybeanls + PropWoodyWets + PropHerbWetls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

###Full and null
BCImod_FullAdd1 <- lmer(CS_BM ~ PropTotWaterls + PropRices + PropSoybeanls + PropWoodyWets + PropHerbWetls + Prop_MedDisturbls + (1|LOC_NUM_BCI), data = BCI30km, REML = F) 

BCImod_null1 <-lmer(CS_BM ~ (1 | LOC_NUM_BCI), data=BCI30km,REML = F)
```

```{r}
##Set up model list for AIC Table###
Cand.BCI <- list()

Cand.BCI[[1]] <- BCImod11
Cand.BCI[[2]] <- BCImod21
Cand.BCI[[3]] <- BCImod31
Cand.BCI[[4]] <- BCImod41
Cand.BCI[[5]] <- BCImod51
Cand.BCI[[6]] <- BCImod61
Cand.BCI[[7]] <- BCImod71
Cand.BCI[[8]] <- BCImod81
Cand.BCI[[9]] <- BCImod91
Cand.BCI[[10]] <- BCImod101
Cand.BCI[[11]] <- BCImod_FullAdd1
Cand.BCI[[12]] <- BCImod_null1
```

```{r}
##AIC Rank Models###
##Note only averaging models with Delta AICc < 4
Modnames <- c("Water + Rice_11",
              "Water + Soy_21",
              "Water + Woody_31",
              "Water + Herb_41",
              "Water + Disturb_51",
              "Water + Rice + Soybean_61",
              "Water + Woody + Herb_71",
              "Water + Rice + Soybean + Disturb_81",
              "Water + Woody + Herb + Disturbance_91",
              "Water + Rice + Soybean + Woody + Herb_101",
              "FullAdd",
              "Null")

aic_table <- aictab(cand.set = Cand.BCI, modnames = Modnames)
aic_table
```

```{r}
##Model-averaging
#Based on AIC results, fit models of interest to a new fit list

Cand.mod_ModAvg <- list()

Cand.mod_ModAvg[[1]] <- BCImod91
Cand.mod_ModAvg[[2]] <- BCImod_FullAdd1
Cand.mod_ModAvg[[3]] <- BCImod71


Modnames_ModAvg <- c("Woody + Herb + Disturbance + Water",
                     "FullAdd",
                     "Woody + Herb + Water")
```

```{r}
modavg_results_Water <- modavg(parm = "PropTotWaterls", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Water
```

```{r}
modavg_results_Herb <- modavg(parm = "PropHerbWetls", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Herb
```

```{r}
modavg_results_Woody <- modavg(parm = "PropWoodyWets", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Woody
```

```{r}
modavg_results_Disturb <- modavg(parm = "Prop_MedDisturbls", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Disturb
```

```{r}
modavg_results_Rice <- modavg(parm = "PropRices", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Rice
```

```{r}
modavg_results_Soy <- modavg(parm = "PropSoybeanls", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Soy
```

###Body Mass Global Model Diagnostics####
```{r}
###Residuals vs fitted of the model
residfitmass <- plot_redres(BCImod_FullAdd1, type = "pearson_cond") +
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Pearson residuals") + xlab("Fitted values")

ggsave(residfitmass, file="residfitmass.jpg", width=35, height=20, units="cm", dpi=300)

###Normality of residuals of the model
residQQplotmass <- plot_resqq(BCImod_FullAdd1) +
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("Normal quantiles")

ggsave(residQQplotmass, file="residQQplotmass.jpg", width=35, height=20, units="cm", dpi=300)

###Residuals vs aginst fixed effects
residmasswat <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd1), y = PropTotWaterls)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Water cover")

residmassrice <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd1), y = PropRices)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Rice")

residmasssoy <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd1), y = PropSoybeanls)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Soybeans")

residmasswood <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd1), y = PropWoodyWets)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Woody wetlands")

residmassherb <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd1), y = PropHerbWetls)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Herbaceous wetlands")

residmassdist <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd1), y = Prop_MedDisturbls)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Disturbance")

##switched off to prevent saving unless needed
#ggsave(residmasswat, file="residmasswat.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residmassrice, file="residmassrice.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residmasssoy, file="residmasssoy.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residmasswood, file="residmasswood.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residmassherb, file="residmassharb.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residmassdist, file="residmassdist.jpg", width=35, height=20, units="cm", dpi=300)
```



###BCI Analysis###
```{r}
##run models
##Note: Restricted Maximum Likelihood REML set to False. REML Fitting is only appropriate for GLMMs (glmer). Since we are using LMM's (lmer), we want the regular Maximum Liklihood (ML) Fitting.

##Rice and Water
BCImod1<-lmer(BCI ~ PropTotWaterls + PropRices + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Soy and Water
BCImod2<-lmer(BCI ~ PropTotWaterls + PropSoybeanls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Woody and Water
BCImod3<-lmer(BCI ~ PropTotWaterls + PropWoodyWets + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Herb and Water
BCImod4<-lmer(BCI ~ PropTotWaterls + PropHerbWetls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Dist and Water
BCImod5<-lmer(BCI ~ PropTotWaterls + Prop_MedDisturbls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Ag Only
BCImod6<-lmer(BCI ~PropTotWaterls + PropRices + PropSoybeanls + (1 | LOC_NUM_BCI), data=BCI30km,REML = F)

#Natural Wetlands
BCImod7 <- lmer(BCI ~ PropTotWaterls + PropWoodyWets + PropHerbWetls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

###Agriculture and Disturbance
BCImod8 <- lmer(BCI ~ PropTotWaterls + PropRices + PropSoybeanls + Prop_MedDisturbls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##Natural Wetlands and Disturbance
BCImod9 <- lmer(BCI ~ PropTotWaterls + PropWoodyWets + PropHerbWetls + Prop_MedDisturbls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

##All Habitat
BCImod10 <- lmer(BCI ~ PropTotWaterls + PropRices + PropSoybeanls + PropWoodyWets + PropHerbWetls + (1|LOC_NUM_BCI), data = BCI30km, REML = F)

###Full and null
BCImod_FullAdd <- lmer(BCI ~ PropTotWaterls + PropRices + PropSoybeanls + PropWoodyWets + PropHerbWetls + Prop_MedDisturbls + (1|LOC_NUM_BCI), data = BCI30km, REML = F) 

BCImod_null<-lmer(BCI ~ (1 | LOC_NUM_BCI), data=BCI30km,REML = F)
```


```{r}
##Set up model list for AIC Table###
Cand.BCI <- list()

Cand.BCI[[1]] <- BCImod1
Cand.BCI[[2]] <- BCImod2
Cand.BCI[[3]] <- BCImod3
Cand.BCI[[4]] <- BCImod4
Cand.BCI[[5]] <- BCImod5
Cand.BCI[[6]] <- BCImod6
Cand.BCI[[7]] <- BCImod7
Cand.BCI[[8]] <- BCImod8
Cand.BCI[[9]] <- BCImod9
Cand.BCI[[10]] <- BCImod10
Cand.BCI[[11]] <- BCImod_FullAdd
Cand.BCI[[12]] <- BCImod_null
```

```{r}
##AIC Rank Models###
##Note only averaging models with Delta AICc < 7
Modnames <- c("Water + Rice_1",
              "Water + Soy_2",
              "Water + Woody_3",
              "Water + Herb_4",
              "Water + Disturb_5",
              "Water + Rice + Soybean_6",
              "Water + Woody + Herb_7",
              "Water + Rice + Soybean + Disturb_8",
              "Water + Woody + Herb + Disturbance_9",
              "Water + Rice + Soybean + Woody + Herb_10",
              "FullAdd",
              "Null")

aic_table <- aictab(cand.set = Cand.BCI, modnames = Modnames)
aic_table
```

##Model-averaging
```{r}
#Based on AIC results, fit models of interest to a new fit list

Cand.mod_ModAvg <- list()

Cand.mod_ModAvg[[1]] <- BCImod9
Cand.mod_ModAvg[[2]] <- BCImod_FullAdd
Cand.mod_ModAvg[[3]] <- BCImod7
Cand.mod_ModAvg[[4]] <- BCImod10


Modnames_ModAvg <- c("Woody + Herb + Disturbance + Water",
                     "FullAdd",
                     "Woody + Herb + Water",
                     "Water + Rice + Soybean + Woody + Herb")
```


```{r}
modavg_results_Water <- modavg(parm = "PropTotWaterls", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Water
```

```{r}
modavg_results_Herb <- modavg(parm = "PropHerbWetls", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Herb
```

```{r}
modavg_results_Woody <- modavg(parm = "PropWoodyWets", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Woody
```

```{r}
modavg_results_Disturb <- modavg(parm = "Prop_MedDisturbls", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Disturb
```

```{r}
modavg_results_Rice <- modavg(parm = "PropRices", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Rice
```

```{r}
modavg_results_Soy <- modavg(parm = "PropSoybeanls", cand.set = Cand.mod_ModAvg, modnames = Modnames_ModAvg)
modavg_results_Soy
```

###BCI Global Model Assumption Checks###
###Assumpotions for body condition
```{r}
###Residuals vs fitted of the model
residfitcondition <- plot_redres(BCImod_FullAdd, type = "pearson_cond") +
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Pearson residuals") + xlab("Fitted values")

ggsave(residfitcondition, file="residfitcondition.jpg", width=35, height=20, units="cm", dpi=300)

###Normality of residuals of the model
residQQplotcondition <- plot_resqq(BCImod_FullAdd) +
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("Normal quantiles")

ggsave(residQQplotcondition, file="residQQplotcondition.jpg", width=35, height=20, units="cm", dpi=300)

###Residuals vs aginst fixed effects
residcondwat <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd), y = PropTotWaterls)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Water cover")

residcondrice <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd), y = PropRices)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Rice")

residcondsoy <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd), y = PropSoybeanls)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Soybeans")

residcondwood <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd), y = PropWoodyWets)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Woody wetlands")

residcondherb <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd), y = PropHerbWetls)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Herbaceous wetlands")

residconddist <- ggplot(BCI30km, aes(x=resid(BCImod_FullAdd), y = Prop_MedDisturbls)) + 
  geom_point() + 
  theme(axis.text.x = element_text(size = 24, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 24, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 34, family = "Times New Roman"),axis.title.x = element_text(size = 34, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Residuals") + xlab("% Disturbance")

##switched off to prevent saving unless needed
#ggsave(residcondwat, file="residcondwat.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residcondrice, file="residcondrice.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residcondsoy, file="residcondsoy.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residcondwood, file="residcondwood.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residcondherb, file="residcondharb.jpg", width=35, height=20, units="cm", dpi=300)
#ggsave(residconddist, file="residconddist.jpg", width=35, height=20, units="cm", dpi=300)
```


###Body Mass Figure Development from Model Averaged Estimates (make sure body mass analysis has been run before running code below)###
```{r}
###Water Cover###
#variable prep

Water.sd <- sd(BCI30km$PropTotWaterl)
Water.mean <-mean(BCI30km$PropTotWaterl)

(0-Water.mean)/(Water.sd)
```

```{r}
#Water Cover Figure
nd <- data.frame(PropTotWaterls=seq(-1.750547, 2.230478, length = 100), PropRices=0, PropSoybeanls=0, PropWoodyWets=0, PropHerbWetls=0,Prop_MedDisturbls=0, LOC_NUM_BCI=NA)
W.act <- modavgPred(cand.set = Cand.mod_ModAvg, newdata = nd)

W.act$Water.log <-nd$PropTotWaterls*Water.sd + Water.mean
W.act$Water.Orig <-exp(W.act$Water.log)
W.act <- as.data.frame(W.act)

WatCov_Graph = ggplot(W.act, aes(x = Water.Orig, y= mod.avg.pred)) + 
  geom_ribbon(aes(ymin = lower.CL, ymax = upper.CL), fill = "grey80") + 
  geom_line(size=1) + 
  theme_classic()  + theme(axis.text.x = element_text(size = 34, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 34, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 44, family = "Times New Roman"),axis.title.x = element_text(size = 44, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Standardized body mass") + xlab("% Water cover")

WatCov_Graph
```

```{r}
###% Woody Wetlands###
max(BCI30km$PropWoodyWets)
min(BCI30km$PropWoodyWets)
```

```{r}
#variable prep
Wood.sd <- sd(BCI30km$PropWoodyWet)
Wood.mean <-mean(BCI30km$PropWoodyWet)
```

```{r}
#Woody Wetlands Figure#
nd <- data.frame(PropTotWaterls=0, PropRices=0, PropSoybeanls=0, PropWoodyWets = seq(-2.677141, 2.021561, length = 100), PropHerbWetls=0,Prop_MedDisturbls=0, LOC_NUM_BCI=NA)
Wo.act <- modavgPred(cand.set = Cand.mod_ModAvg, newdata = nd)

Wo.act$Wood.Orig <-nd$PropWoodyWets*Wood.sd + Wood.mean
Wo.act <- as.data.frame(Wo.act)

Wood_Graph = ggplot(Wo.act, aes(x = Wood.Orig, y= mod.avg.pred)) + 
  geom_ribbon(aes(ymin = lower.CL, ymax = upper.CL), fill = "grey80") + 
  geom_line(size=1) + 
  theme_classic()  + theme(axis.text.x = element_text(size = 34, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 34, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 44, family = "Times New Roman"),axis.title.x = element_text(size = 44, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Standardized body mass") + xlab("% Woody wetlands")

Wood_Graph
```

```{r}
###% Herb Wetlands###
max(BCI30km$PropHerbWetls)
min(BCI30km$PropHerbWetls)
```

```{r}
#variable prep
Herb.sd <- sd(BCI30km$PropHerbWetl)
Herb.mean <-mean(BCI30km$PropHerbWetl)
```

```{r}
#Herbaceous Wetland Figure
nd <- data.frame(PropTotWaterls=0, PropRices=0, PropSoybeanls=0, PropWoodyWets=0, PropHerbWetls=seq(-4.615127, 2.369486, length = 100),Prop_MedDisturbls=0, LOC_NUM_BCI=NA)
H.act <- modavgPred(cand.set = Cand.mod_ModAvg, newdata = nd)

H.act$Herb.log <-nd$PropHerbWetls*Herb.sd + Herb.mean
H.act$Herb.Orig <-exp(H.act$Herb.log)
H.act <- as.data.frame(H.act)

Herb_Graph = ggplot(H.act, aes(x = Herb.Orig, y= mod.avg.pred)) + 
  geom_ribbon(aes(ymin = lower.CL, ymax = upper.CL), fill = "grey80") + 
  geom_line(size=1) + 
  theme_classic()  + theme(axis.text.x = element_text(size = 34, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 34, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 44, family = "Times New Roman"),axis.title.x = element_text(size = 44, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Standardized body mass") + xlab("% Herbaceous wetlands")

Herb_Graph
```

```{r}
###% Disturbance###
max(BCI30km$Prop_MedDisturbls)
min(BCI30km$Prop_MedDisturbls)
```

```{r}
#variable prep
Dist.sd <- sd(BCI30km$Prop_MedDisturbl)
Dist.mean <-mean(BCI30km$Prop_MedDisturbl)
```

```{r}
#Disturbance Figure
nd <- data.frame(PropTotWaterls=0, PropRices=0, PropSoybeanls=0, PropWoodyWets=0, PropHerbWetls=0,Prop_MedDisturbls=seq(-3.42827, 4.005376, length = 100), LOC_NUM_BCI=NA)
D.act <- modavgPred(cand.set = Cand.mod_ModAvg, newdata = nd)

D.act$Dist.log <-nd$Prop_MedDisturbls*Dist.sd + Dist.mean
D.act$Dist.Orig <-exp(D.act$Dist.log)
D.act <- as.data.frame(D.act)

Dist_Graph = ggplot(D.act, aes(x = Dist.Orig, y= mod.avg.pred)) + 
  geom_ribbon(aes(ymin = lower.CL, ymax = upper.CL), fill = "grey80") + 
  geom_line(size=1) + 
  theme_classic()  + theme(axis.text.x = element_text(size = 34, color = "black", family = "Times New Roman"), axis.text.y = element_text(size = 34, color = "black", family = "Times New Roman"), axis.title.y = element_text(size = 44, family = "Times New Roman"),axis.title.x = element_text(size = 44, family = "Times New Roman"), panel.background = element_rect(fill = "white"), panel.border = element_rect(colour = "black", fill = "NA")) + ylab("Standardized body mass") + xlab("% Disturbance")

Dist_Graph
```

###Body Mass Predictions for GIS Map Reclassifications###
```{r}
###Water Cover
Water.sd <- sd(BCI30km$PropTotWaterl)
Water.mean <-mean(BCI30km$PropTotWaterl)


(log(0.01)-Water.mean)/Water.sd
(log(100)-Water.mean)/Water.sd
```

```{r}
#generate predictions
nd <- data.frame(PropTotWaterls=seq(-36.0666, 6.429668, length = 1000), PropRices=0, PropSoybeanls=0, PropWoodyWets=0, PropHerbWetls=0,Prop_MedDisturbls=0, LOC_NUM_BCI=NA)
W.act <- modavgPred(cand.set = Cand.mod_ModAvg, newdata = nd)

W.act$Water.log <-nd$PropTotWaterls*Water.sd + Water.mean
W.act$Water.Orig <-exp(W.act$Water.log)
W.act <- as.data.frame(W.act)
```

```{r}
#Woody wetlands
Wood.sd <- sd(BCI30km$PropWoodyWet)
Wood.mean <-mean(BCI30km$PropWoodyWet)

(0.01-Wood.mean)/Wood.sd
(100-Wood.mean)/Wood.sd
```

```{r}
#generate predictions
nd <- data.frame(PropTotWaterls=0, PropRices=0, PropSoybeanls=0, PropWoodyWets = seq(-3.634932, 46.68695, length = 1000), PropHerbWetls=0,Prop_MedDisturbls=0, LOC_NUM_BCI=NA)
Wo.act <- modavgPred(cand.set = Cand.mod_ModAvg, newdata = nd)

Wo.act$Wood.Orig <-nd$PropWoodyWets*Wood.sd + Wood.mean
Wo.act <- as.data.frame(Wo.act)
```

```{r}
#Herbaceous wetlands
Herb.sd <- sd(BCI30km$PropHerbWetl)
Herb.mean <-mean(BCI30km$PropHerbWetl)

(log(0.01)-Herb.mean)/Herb.sd
(log(100)-Herb.mean)/Herb.sd
```

```{r}
#generate predictions
nd <- data.frame(PropTotWaterls=0, PropRices=0, PropSoybeanls=0, PropWoodyWets=0, PropHerbWetls=seq(-13.12833, 24.09572, length = 1000),Prop_MedDisturbls=0, LOC_NUM_BCI=NA)
H.act <- modavgPred(cand.set = Cand.mod_ModAvg, newdata = nd)

H.act$Herb.log <-nd$PropHerbWetls*Herb.sd + Herb.mean
H.act$Herb.Orig <-exp(H.act$Herb.log)
H.act <- as.data.frame(H.act)
```

```{r}
#Disturbance
Dist.sd <- sd(BCI30km$Prop_MedDisturbl)
Dist.mean <-mean(BCI30km$Prop_MedDisturbl)

(log(0.01)-Dist.mean)/Dist.sd
(log(100)-Dist.mean)/Dist.sd
```

```{r}
#generate predictions
nd <- data.frame(PropTotWaterls=0, PropRices=0, PropSoybeanls=0, PropWoodyWets=0, PropHerbWetls=0,Prop_MedDisturbls=seq(-12.77981, 17.80551, length = 1000), LOC_NUM_BCI=NA)
D.act <- modavgPred(cand.set = Cand.mod_ModAvg, newdata = nd)

D.act$Dist.log <-nd$Prop_MedDisturbls*Dist.sd + Dist.mean
D.act$Dist.Orig <-exp(D.act$Dist.log)
D.act <- as.data.frame(D.act)
```

###Save csv's to desired filepath (note: everytime above prediction code is run, it may vary slightly. This is due to parametric bootstrapping techniques required of mixed-model predictions)###
```{r}
write.csv(W.act,file='/filepath/WaterMapData_11132022.csv', row.names=FALSE)

write.csv(Wo.act,file='/filepath/WoodyMapData_11132022.csv', row.names=FALSE)

write.csv(H.act,file='/filepath/HerbaceousMapData_11132022.csv', row.names=FALSE)

write.csv(D.act,file='/filepath/DisturbanceMapData_11132022.csv', row.names=FALSE)
```
